---
title: "Put a real title here"
subtitle: "SDS 192: MP3"
author: "Your name"
date: "`r format(Sys.Date(), '%B %e, %Y')`"
output: 
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true
    fig_width: 7
    fig_height: 6
    fig_caption: true
    theme: lumen
    df_print: paged
    code_folding: show
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  message = FALSE,
  echo = TRUE,
  warning = FALSE
)
library(tidyverse)
library(sds192)
```

## Introduction

> READ THE INSTRUCTIONS: https://beanumber.github.io/sds192/mod_babynames.html

Your goal is to recreate this data graphic as closely as you can:

## Loading the data

```{r, message=FALSE}
library(babynames)
```

### Hard-coded list of names

You might find this list of names helpful for debugging. 
However, you should **not** use these in your final graphic -- your goal is to generate the correct list of names algorithmically.

```{r}
fd_names <- c(
  "Jessie", "Marion", "Jackie", "Alva", "Ollie",
  "Jody", "Cleo", "Kerry", "Frankie", "Guadalupe",
  "Carey", "Tommie", "Angel", "Hollis", "Sammie",
  "Jamie", "Kris", "Robbie", "Tracy", "Merrill",
  "Noel", "Rene", "Johnnie", "Ariel", "Jan",
  "Devon", "Cruz", "Michel", "Gale", "Robin",
  "Dorian", "Casey", "Dana", "Kim", "Shannon"
) %>%
  enframe(name = "fd_rank", value = "name")
glimpse(fd_names)
```

## Word count

```{r word_count, message=FALSE, echo=FALSE}
text_stats()
```

## Standards

In this assignment, we are attempting the following standards:

```{r buttons, echo=FALSE}
standard_button("markdown")
standard_button("aesthetics")
standard_button("wrangling")
standard_button("context")
standard_button("reshape")
standard_button("relational")
standard_button("ethics")
standard_button("github")
standard_button("iteration")
standard_button("function")
```


